\textbf{Vision statement.} A short presentation and extended discussion about the purpose of the workshop and the larger initiative towards better infrastructure for open community data science.

\textbf{Hack session.} Participants (split into teams) work on the replication/extension task.  Participants will have a total of 4.5 hours' time on task besides introduction, breaks, and reflection time.  The workshop organizers will work with participants to both answer their questions and observe their work.

\textbf{Reporting and reflection.} Participant teams report on their progress and reflect on what did and did not work for them.  We will specifically ask how the methods description, querying system, and metadata was helpful and how.

\subsubsection{Schedule (tentative)}
\begin{itemize}
\item 8:15-9:00: breakfast mingling
\item 9:00 (sharp!): Intro to the day (process + brief task overview)
\item 9:10-10:00: Vision statement about Infrastructure for OOC studies
\item 10:00-10:15: Data introduction -- Each team/table reviews the task, documentation and infrastructure.
\item 10:15-10:30: coffee break, email breaktime
\item 10:30-12:00: Morning hack session breakouts (one team per table)
\item 12:00-12:30: Lunch serving, email breaktime
\item 12:30-3:15: Afternoon hack session breakouts (one team per table)
\item 3:15-3:30: coffee break, email breaktime
\item 3:30-4:30: Report-out and reflection
\item 4:30: Wrap-up, Thanks \& Next steps.
\item 5:00: Dinner discussion \& share contacts.
\end{itemize}
