OOC research has advanced considerably in the last few decades, but it is still difficult to compare and contrast research findings from different pieces of work.   Part of this is due to the very nature of the research; it comes from all sort of fields from information systems (e.g. \cite{ma07through}) to computer science (e.g. \cite{shneiderman00creating}) to information science (e.g. \cite{preece00online}) to marketing (e.g. \cite{kozinets02field}), and is studied in a wide variety of platforms from Twitter (e.g. \cite{vieweg10microblogging}) to Wikis (e.g. \cite{beschastnikh08wikipedian}) to question-and-answer forums (e.g. \cite{zhang07expertise}).  As a result, different disciplines and study venues use different language and descriptions, making it hard to integrate knowledge gleaned from disparate origins.

Moreover, the lack of easy translatability between fields and platforms has made the reproducing of findings difficult.  A researcher in one field use a definition used or understood the same way in another field.  For example, it's difficult for a researcher who works with Flickr data to understand how certain concepts are operationalized by researchers who work with blogging data. The field has progressed fine up until this point because there is so much research to do in this space, but now is the time to start building a cohesive theory of online communities and to create knowledge built on top of other knowledge, and to provide standards that allow different researchers to reproduce each others' findings.

In order to take the field to the next step, it is necessary to develop a standard of communication that will allow different researchers to communicate how and why they performed their analysis and research the way that they did.  One development in other interdisciplinary fields that has helped communication across boundaries is the creation of a uniform methods protocol (e.g. \cite{grimm10odd}).  By creating standards that describe how data is collected and analyzed, as well as how certain measurements in the theory are operationalized within the data, it is possible to make it easier for different researchers to understand each other's work and to reproduce findings.
